Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-05-15 paper/manuscript.tex
attempts were made

To better understand this problem, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue. Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.

{[}Prior sentence needs work{]}

A few large-scale investigations have measured replication rates in samples of psychology studies. Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs. They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). ManyLabs investigated heterogeneity using short target studies that compared between two conditions each. These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites. Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported. In this well-resourced environment with expert input, the replication rate was around 60\%.

@@

@@

Our goal in estimating replicability is to look for markers of when findings can support cumulative science. Most scientific work is conducted by students, working with limited budgets, limited time, and without access to outside experts. Therefore, to figure out what studies graduate students could build on, it makes sense to focus on replications conducted by students (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}). In our current study, we use student success at replicating an effect as our estimand. In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.

{[}maybe drop last sentence and work into a longer paragraph?{]}

{[}TODO Maya says firm this up and introduce quant outcomes as well{]}

As a complement, we also measure how similar/consistent the original and replication effects were for the key effect of each study. TODO blah blah

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. We use a subjective replication score as our primary metric. Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p\textless.05 same direction as original). This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies. As a complement to this, we include two statistical measures of replication success, applied to the key stat TODO

{[}Examples ??{]} TODO redo paragraph
Despite variation in how large-scale replication studies have defined replication successes, there is work suggesting some consistency in the predictors of replication success. Knowing these predictors is important for appropriately calibrating how we read the literature and for eventually identifying targets for interventions.

{[}TODO Maya possibly suggests mentioning the uzzi paper that I am dubious of{]}
Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019}), but have not identified concrete predictors that differentiate replications from non-replications. Machine learning approaches also are above chance at predicting replication, but this did not identify interpretable predictors TODO CITATIONS In terms of specific attributes that predict replicability, Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate. One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.

Experimental approaches can be used to test potential interventions. Protzko et al. (\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original. Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.

Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability. Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. More data is needed to identify markers of replicability and targets for potential future interventions.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.

@@

Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure. This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample. Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class. For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's \(\rho\): 0.88, disagreement in 26\% of cases).

As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}). We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect. Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect would be interpreted as non-replications. Thus, this metric may not always match researcher intuitions on whether the effect is replicating. TODO NEEDS WORK

@@

Across the 176 studies, the average subjective replication score was 49\%, which we interpret as an overall subjective replication rate. 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication.

@@

Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data. Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

TODO describe what we did to get these numbers! Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies. Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much. Studies with multiple vignettes replicated 2.62 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe prior (see Methods for details; see Supplement for all estimates from all models). We ran models both using all the original-replication pairs, but without the predictors original effect size and original p value (that were uncodable for some studies), and models including all predictors, but limiting to the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

Within-subjects designs stand out as the strongest indicator of replicability in the model with all the original-replication pairs (0.55, CrI= {[}-0.01, 2{]}). In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}). Standardized effect size is another strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models. The strongest predictors were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).

@@

The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances. Thus, we believe it is relevant to consider how well studies replicate under the limitations of real world resource and expertise constraints.

We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole. Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-) replication, but only as correlational markers. Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original. For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design. Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.

@@

This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure. As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p\_original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}). p\_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution. Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.

@@

We then calculated p values, ES, p\_orig, and predInt. We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent. The means and test statistics are more likely to have been outputted programmatically and copied directly into the text. In contrast, p-values are often reported as \textless.001 rather than as a point value, and effect size derivations may be error prone. By recording the raw statistics we used and using our available code to calculate other measures, we are transparent, as the test statistics can be searched for in the papers, and all processing is documented in code.

In some cases, p-values and or effect sizes were not calculable either due to insufficient reporting (ex. reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex. PCA as measure of interest). Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p\_original and prediction interval.

@@

All models used a horseshoe prior in brms. All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students. We did not include any interaction terms in the models. All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior. The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating amazon's mechanical turk as a tool for experimental behavioral research. \emph{{PLOS} {ONE}} \textbf{8}:e57410. doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}

@@

\leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, Brand R, Brandt MJ, Brewer G, Bruyneel S, Calvillo DP, Campbell WK, Cannon PR, Carlucci M, Carruth NP, Cheung T, Crowell A, De Ridder DTD, Dewitte S, Elson M, Evans JR, Fay BA, Fennis BM, Finley A, Francis Z, Heise E, Hoemann H, Inzlicht M, Koole SL, Koppel L, Kroese F, Lange F, Lau K, Lynch BP, Martijn C, Merckelbach H, Mills NV, Michirev A, Miyake A, Mosser AE, Muise M, Muller D, Muzi M, Nalis D, Nurwanti R, Otgaar H, Philipp MC, Primoceri P, Rentzsch K, Ringos L, Schlinkert C, Schmeichel BJ, Schoch SF, Schrama M, Schütz A, Stamos A, Tinghög G, Ullrich J, vanDellen M, Wimbarti S, Wolff W, Yusainy C, Zerhouni O, Zwienenberg M (2016) A multilab preregistered replication of the ego-depletion effect. \emph{Perspect Psychol Sci} \textbf{11}:546--573. doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}

@@

\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
Open Science Consortium (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}. \emph{Science}

@@

>>>>

To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability. Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.

{[}Prior paragraph may still need work{]}

A few large-scale investigations have measured replication rates in samples of psychology studies. Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participating labs. They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). Many Labs investigated heterogeneity using short target studies that compared between two conditions each. These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites. Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported. In this well-resourced environment with expert input, the replication rate was around 60\%.

@@

{[}Prior paragraph is a bit verbose, but it's probably fine{]}

@@

Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science. If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either. Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}). Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).

{[}TODO possibly say more??{]}

Despite variation in the methods and outcomes used by large-scale replication studies, they are often aggregated together in analyses looking at the predictablity of replication success. Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019}), but have not identified concrete predictors that differentiate replications from non-replications. Machine learning approaches trained on the available replications are also above chance at predicting replication success (\protect\hyperlink{ref-yang2020}{Yang et al. 2020}, \protect\hyperlink{ref-youyou2023}{Youyou et al. 2023}). In terms of specific attributes that predict replicability, Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019}) examined statistical and demographic features of studies and identified larger sample sizes, larger effect sizes, and simple effects (as opposed to interaction terms) as predictive of replication, and Open Science Consortium (\protect\hyperlink{ref-openscienceconsortium2015}{2015}) looked at correlates of replicability in the RP:P sample and found that studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate. One potential set of correlates to replicability that has not been thoroughly examined are experimental design features, such as between or within subjects designs and repeated measures.

{[}TODO is there a citation for experimental design features being possibly relevant?{]}

While most approaches to correlates of replicability have been correlational, experimental approaches can be used to test potential interventions. Protzko et al. (\protect\hyperlink{ref-protzko2020}{2020}) showed, across 16 studies, that better methodological practices led to replication rates that matched theoretical expectations with replication effect sizes comparable with the original. Many Labs 5 added expert (original author) advice to a replication process, and found that it did not substantially increase the replication rate for the 10 studies (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). These types of experiments are valuable for testing potential causes of non-replication, but they don't scale well due to expense, and not all influences on non-replication may be experimentally manipulable.

{[}Awkward transition{]}

However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications. As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigate statistical and experimental-design predictors of replicability in this dataset and find that within-subjects designs and studies with large standardized effect sizes are positively correlated with replication success.

@@

Of note, these replications were all conducted on short time scales, with constrained budgets, that in some cases limited the number of participants who could be recruited below what the original study had or what power analyses suggested. In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (default 2011-2020) or Prolific (default 2021-2022).

Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). However, whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p\textless.05 same direction as original). As our primary outcome, we use a subjective replication score which, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample. Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class. For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (inter-rater reliability, Spearman's \(\rho\): 0.88, disagreement in 26\% of cases).

As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}). We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). The prediction interval depends on the level of evidence of the original study; if the effect was marginal, the prediction interval could overlap zero; thus, a replication might fall within the predictive interval, and be consistent with the original outcome, but not provide compelling evidence for the claimed effect. Conversely, large original effects with precise point estimates may have prediction intervals that do not overlap a smaller replication effect size, and thus would be inconsistent with the original outcome, even though researcher intuition might classify it as a success. Thus, the statistical metrics quantify the similarity of a key statistic, but they will not always match researcher intuitions on whether a study replicated.

@@

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication. This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).

@@

TODO any citations around experimental design predictors??

Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data. Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. To quantify the effects of these single predictors, we ran logistic models predicting the subjective replication score (on 0-1) as a function of the single predictor, and exponentiated the coefficient to get an odds ratio. Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated 2.45 times as often as social psychology studies. Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much. Studies with multiple vignettes replicated 2.62 times as often as single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al. 2009}). We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results. Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.55, CrI= {[}-0.01, 2{]}). In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}), and standardized effect size is also a strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models. The strongest predictors for prediction interval were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).

@@

We conducted an observational study of replication attempts, and our results are limited by the studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole. Our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers. Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original. For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design. Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.

{[}TODO should we discuss the need for more replications and pooling and coding??{]}

@@

This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure. As a complement, we also identified a ``key'' statistical test for each paper (see below for details), and if possible, computed p-original and prediction interval at this statistic, following Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}). p-original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution. Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.

@@

We then calculated p values, effect sizes, p-original, and prediction intervals. We choose to recalculate p values and effect sizes from the means or test statistic rather than use reported measures when possible because we thought this would be more reliable and transparent. The means and test statistics are more likely to have been outputted programmatically and copied directly into the text. In contrast, p-values are often reported as \textless.001 rather than as a point value, and effect size derivations may be error prone. By recording the raw statistics we used and using our available code to calculate other measures, we are transparent, as the test statistics can be searched for in the papers, and all processing is documented in code.

In some cases, p-values or effect sizes were not calculable either due to insufficient reporting (ex. reporting a p-value but no other statistics from a test) or key measures where p-values and effect sizes did not apply (ex. PCA as measure of interest). Where studies reported beta estimates and standard errors or proportions, standardized effects sizes are not an applicable measure, but we were still able to calculate p-original and prediction interval.

@@

We used a horseshoe shrinkage prior on the fixed effect coefficients because we had a lot of predictors compared to the amount of data (\protect\hyperlink{ref-carvalho09}{Carvalho et al. 2009}). All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students. We did not include any interaction terms in the models. All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior. The priors we used were horseshoe(3) for betas, normal(0,.5) for standard deviation of random slopes, and lkj(1) for correlations between random slopes. Models were run in BRMS (\protect\hyperlink{ref-brms}{Bürkner 2017}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-brms}{}}%
Bürkner P-C (2017) {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software} \textbf{80}:1--28. doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01}

@@

\leavevmode\vadjust pre{\hypertarget{ref-carvalho09}{}}%
Carvalho CM, Polson NG, Scott JG (2009) Handling sparsity via the horseshoe. In: Dyk D van, Welling M (eds) \emph{Proceedings of the twelth international conference on artificial intelligence and statistics}. PMLR, Hilton Clearwater Beach Resort, Clearwater Beach, Florida USA, p 73--80. Available from: \url{https://proceedings.mlr.press/v5/carvalho09a.html}

\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research}. \emph{PLOS ONE} \textbf{8}:e57410. doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}

@@

\leavevmode\vadjust pre{\hypertarget{ref-hagger2016}{}}%
Hagger MS, Chatzisarantis NLD, Alberts H, Anggono CO, Batailler C, Birt AR, Brand R, Brandt MJ, Brewer G, Bruyneel S, Calvillo DP, Campbell WK, Cannon PR, Carlucci M, Carruth NP, Cheung T, Crowell A, De Ridder DTD, Dewitte S, Elson M, Evans JR, Fay BA, Fennis BM, Finley A, Francis Z, Heise E, Hoemann H, Inzlicht M, Koole SL, Koppel L, Kroese F, Lange F, Lau K, Lynch BP, Martijn C, Merckelbach H, Mills NV, Michirev A, Miyake A, Mosser AE, Muise M, Muller D, Muzi M, Nalis D, Nurwanti R, Otgaar H, Philipp MC, Primoceri P, Rentzsch K, Ringos L, Schlinkert C, Schmeichel BJ, Schoch SF, Schrama M, Schütz A, Stamos A, Tinghög G, Ullrich J, vanDellen M, Wimbarti S, Wolff W, Yusainy C, Zerhouni O, Zwienenberg M (2016) A {Multilab Preregistered Replication} of the {Ego-Depletion Effect}. \emph{Perspect Psychol Sci} \textbf{11}:546--573. doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}

@@

\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
Open Science Consortium (2015) Estimating the reproducibility of psychological science. \emph{Science}

@@

\leavevmode\vadjust pre{\hypertarget{ref-yang2020}{}}%
Yang Y, Youyou W, Uzzi B (2020) Estimating the deep replicability of scientific findings using human and artificial intelligence. \emph{Proc Natl Acad Sci} \textbf{117}:10762--10768. doi:\href{https://doi.org/10.1073/pnas.1909046117}{10.1073/pnas.1909046117}

\leavevmode\vadjust pre{\hypertarget{ref-youyou2023}{}}%
Youyou W, Yang Y, Uzzi B (2023) A discipline-wide investigation of the replicability of {Psychology} papers over the past two decades. \emph{Proc Natl Acad Sci} \textbf{120}:e2208863120. doi:\href{https://doi.org/10.1073/pnas.2208863120}{10.1073/pnas.2208863120}
